\section{The IMDb Dataset}
\label{sec:foundamentals:dataset}
The IMDb, an US-based company owned by Amazon.com, provides free access to its
famous dataset of cinema, TV movies and series for research purposes at its
website:~\url{http://www.imdb.com/interfaces}. IMDb's data is modularly grouped
by information type (such as ``business'', ``biography'', ``plot''). Each data
module is provided in a compressed CSV (Comma Separated Values) text file.
Hence, reconstructing the required parts of the original dataset requires only
a subset of the data modules.

The original dataset can be built as a SQL database from its constituent
data-modules using the \texttt{imdbpy2sql} script, available from the IMDbPY
tool\footnote{IMDbPY\@: \url{http://imdbpy.sourceforge.net/}}. This software
includes many features for accessing and querying the built SQL database.

The IMDb dataset describes movies and their full cast and crew in extensive
detail, including movie alternate names, associated keywords, references to
other movies, gross (revenue), box office, runtime in minutes,
genres\footnote{One or more out of 21 possible genres can be assigned to a
movie. The complete IMDb genre list is available at
\url{http://www.imdb.com/genre/}.}, plot, production budget, audio and color
schemes, production countries and certificate ratings for various
countries\footnote{Each country has a legal entity responsible for issuing
movie certificates. In the United States, it is the MPAA (Motion Picture
Association of America:~\url{http://www.mpaa.org/film-ratings/}).}. It also
contains extra information about the companies that worked in several aspects
of the movie such as special effects, sound mix and distribution. It lists
movie producers, writers, directors, editors, soundtrack composers, actors and
actresses, makeup personal, and even stunt actors. For each of these people,
more information such as full name, short biography, birth date, birth city and
height is sometimes available.

Anyone can register at IMDb and vote for any title in the database by grading
it in a scale of [1--10] once. IMDb datasets also include movie
\textit{ratings} as weighted averages of all votes\footnote{Ratings are
different from \textit{reviews}, which are more elaborate opinions provided by
registered users.} and the absolute number of \textit{votes} movies received.
Most movies in the IMDb database are from virtually unknown productions, i.e.\@
they received very little or no user ratings and reviews. More than half the
movies in the database received less than 30 votes, whereas all professionally
produced movies typically receive several thousands \textit{votes}.

Here, the full IMDb dataset was downloaded in November 2014. At that
time, it contained information of movies from the late 1800's to 2014, from all
over the world, totalling approximately 1.4~gigabytes of data. Movies
from 2014 were recently added to the dataset, and could have missing or
unstable data. Therefore, movies from 2014 were not considered.
