\section{Final Considerations}
\label{sec:related_final}
We aim to forecast movie success parameters. However, besides financial
success, we also plan to predict popularity and ratings from movies by
considering social features from movie producers and a larger set of movies in
our analysis. The aforementioned studies (and others that relate network
topology and team performance) consider very small datasets. Unlike them, we
make an extensive analysis of social features from teams by exploring a large
set of 12,250 movies.

In social network analysis, considering such larger datasets is critical in
order to yield more robust results. Our dataset is assembled from the whole set
of feature-length cinema movies in the IMDb dataset that received at least
1,000 votes.  It is composed by several movie genres, spanning several decades
and coming from a wide range of countries. This way, our study considers more
comprehensive and heterogeneous information regarding teamwork than any of the
previous work.

Furthermore, we also include features used by these studies in our analysis,
whenever data was available in the IMDb dataset. Some data (such as genres) is
easily available, whereas others (such as marketing expenses) are hard to
obtain.  Social features are used in addition to all other features in a very
similar way as the prediction task presented by~\cite{COSN2013}.

To the best of our knowledge, we are the first to study the relation between
network topology aspects and success by considering such a large network of
motion pictures producers.
