Teamwork is present in virtually all important activities in society, such as
movie and show production, scientific research, sports and corporate offices.
In most cases, agents working in the same industry organize themselves in a
social network, and teams are formed in a non-random way according to this
network. In collaborative work, agents must choose their team, preferably
according to a strategy that maximizes the odds of forming a high-achieving
team. In this thesis, considering the task of forecasting success of a team in
the context of a social network, we assess the predictive power of purely
social characteristics from teams in comparison to other non-social
characteristics knowingly correlated with team success. In contrast to previous
works on forecasting or evaluating the impact of social characteristics in team
success, our approach considers multiple social characteristics and a large
number of different teams in the context of a large social network. Our
approach uses historical co-production data from movies to assemble a graph
representing the social network of movie producing agents. It extracts several
topological and non-topological characteristics from movie-producing teams
according to this graph. Finally, it assesses the predictive power of
topological characteristics being studied and presents insights on how such
results can be used to compose better teams. Our results show that some
topological characteristics from teams help forecasting team success,
complementing non-topological characteristics already known to correlate with
higher-achieving teams.

\keywords{Social Networks, Team Formation, Regression analysis, Success
Prediction}
